---
title: "Experiments for 'Feature Attribution for Survival Neural Networks'
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  out.width = "100%"
)
```

```{r setup}
library(Survinng)
library(ggplot2)
library(dplyr)
library(tidyr)
library(SurvMetrics)
library(survival)
library(simsurv)
library(survminer)

# figure path
fig_path <- here::here("figures_paper")
if (!file.exists(fig_path))
  dir.create(fig_path)
fig <- function(x)
  here::here(fig_path, x)
```

### Time-independent effects

## Generate the data

Simulation setting:
- $10,000$ samples ($9,500$ for training, $500$ for testing)
- No time-dependent effects
- $X_1 \sim \mathcal{N}(0,1)$ has a positive effect on the hazard -> negative effect on survival
- $X_2 \sim \mathcal{U}(0,1)$ has a stronger negative effect on the hazard -> positive effect on survival
- $X_3 \sim \mathcal{U}(-1,1)$ has no effect

```{r tid data generation}
set.seed(42)

# Simulate data
n <- 10000
x <- data.frame(x1 = rnorm(n), x2 = runif(n, 0, 1), x3 = runif(n, -1, 1))
simdat <- simsurv(dist = "weibull", lambdas = 0.1, gammas = 2.5, betas = c(x1 = 1.7, x2 = -2.4),
                  x = x, maxt = 7)
y <- simdat[, -1]
colnames(y)[1] <- "time"
dat <- cbind(y, x)

# Train/test
idx <- sample(n, 9500)
train <- dat[idx, ]
test <- dat[-idx, ]
```

## Fit the models
```{r tid, echo = FALSE}
fit_model <- function(model, train, test) {
  callr::r(function(model, train, test) {
    library(survivalmodels)
    library(survival)
    reticulate::use_condaenv("Survinng", required = TRUE)
    set.seed(1)
    set_seed(1)
    
    # Fit model
    if (model == "CoxTime") {
      model <- coxtime(Surv(time, status) ~ ., data = train, verbose = FALSE, epochs = 500L,
                     early_stopping = TRUE, frac = 0.33, batch_size = 1024L, patience = 10L,
                     dropout = 0.1)
    } else if (model == "DeepHit") {
      model <- deephit(Surv(time, status) ~ ., data = train, verbose = FALSE, epochs = 500L,
                     early_stopping = TRUE, frac = 0.33, patience = 10L, cuts = 30, 
                     batch_size = 1024L, dropout = 0.1)
    } else if (model == "DeepSurv") {
      model <- deepsurv(Surv(time, status) ~ ., data = train, verbose = FALSE, epochs = 100L,
                      early_stopping = TRUE, frac = 0.33, patience = 10L, batch_size = 1024L,
                      dropout = 0.1)
    } else {
      stop("Model not found")
    }
    
    # Make predictions
    pred <- predict(model, newdata = test, type = "survival")
    dat <- data.frame(
      pred = c(pred), 
      time = rep(as.numeric(colnames(pred)), each = nrow(pred)),
      id = rep(1:nrow(pred), ncol(pred))
    )
    list(Survinng::extract_model(model), pred = dat)
  }, list(model, train, test))
}
```

```{r tid fit models, fig.width=10, fig.height=15}
# Fit the models
ext_deephit <- fit_model("DeepHit", train, test)
ext_coxtime <- fit_model("CoxTime", train, test)
ext_deepsurv <- fit_model("DeepSurv", train, test)
```


## Create Explainer

```{r tid explainer}
library(Survinng)
library(torch)

# Create explainer
exp_deephit <- Survinng::explain(ext_deephit[[1]], data = test)
exp_coxtime <- Survinng::explain(ext_coxtime[[1]], data = test)
exp_deepsurv <- Survinng::explain(ext_deepsurv[[1]], data = test)
```


## Performance Measures

```{r tid performance measures, fig.width=8, fig.height=8}
# Define a function to reshape data into a wide matrix format
prepare_matrix <- function(data, id_col = "id", time_col = "time", pred_col = "pred") {
  wide_data <- data %>%
    pivot_wider(names_from = {{time_col}}, values_from = {{pred_col}})
  
  # Convert the specified column to row names and remove it from the data
  wide_data <- as.data.frame(wide_data)
  rownames(wide_data) <- wide_data[[id_col]]
  wide_data <- wide_data[, -which(names(wide_data) == id_col)]
  
  # Convert to a matrix
  as.matrix(wide_data)
}

# Prepare matrices
matrix_coxtime <- prepare_matrix(ext_coxtime$pred)
matrix_deepsurv <- prepare_matrix(ext_deepsurv$pred)
matrix_deephit <- prepare_matrix(ext_deephit$pred)[,-1]

# Define survival object
surv_obj <- Surv(test$time, test$status)

# Define time indices and sampled time
t_interest <- sort(unique(ext_coxtime$pred$time))
num_samples <- 100
indices <- round(seq(1, length(t_interest), length.out = num_samples))
sampled_t <- t_interest[indices]
deephit_t <- sort(unique(ext_deephit$pred$time))[-1]

# Sample matrices
sampled_matrix_coxtime <- matrix_coxtime[, indices]
sampled_matrix_deepsurv <- matrix_deepsurv[, indices]

# Calculate Brier scores in a single step
calculate_brier <- function(matrix, times, surv_obj) {
  sapply(1:ncol(matrix), function(i) Brier(surv_obj, pre_sp = matrix[, i], times[i]))
}

metrics_coxtime <- calculate_brier(sampled_matrix_coxtime, sampled_t, surv_obj)
metrics_deepsurv <- calculate_brier(sampled_matrix_deepsurv, sampled_t, surv_obj)
metrics_deephit <- calculate_brier(matrix_deephit, deephit_t, surv_obj)

# Combine results into a single data frame for plotting
combine_results <- function(metrics, times, model_name) {
  data.frame(time = times, BS = metrics, model = model_name)
}

data_coxtime <- combine_results(metrics_coxtime, sampled_t, "CoxTime")
data_deepsurv <- combine_results(metrics_deepsurv, sampled_t, "DeepSurv")
data_deephit <- combine_results(metrics_deephit, deephit_t, "DeepHit")
data_BS <- rbind(data_coxtime, data_deepsurv, data_deephit)

# Plot Brier scores
colorblind_palette <- c("CoxTime" = "#E69F00", "DeepSurv" = "#56B4E9", "DeepHit" = "#009E73")

brier_plot_tid <- ggplot(data_BS, aes(x = time, y = BS, color = model, linetype = model)) +
  geom_line() +
  scale_color_manual(values = colorblind_palette) +  # Apply custom colors
  scale_linetype_manual(values = c("CoxTime" = "solid", "DeepSurv" = "dashed", "DeepHit" = "dotted")) + 
  labs(title = "Brier Score over Time", x = "Time", y = "Brier Score") +
  theme_minimal(base_size = 16)
brier_plot_tid 

# Save plot
ggsave(
  "/Users/sophielangbein/Desktop/PhD/Survinng/plots_paper/brier_plot_tid.pdf",
  plot = brier_plot_tid,
  width = 8,
  height = 8,
  device = "pdf"
)

# Calculate C-index and IBS for each model
calculate_cindex <- function(matrix, surv_obj, index) {
  Cindex(surv_obj, predicted = matrix[, index])
}

calculate_ibs <- function(matrix, times, surv_obj) {
  IBS(surv_obj, sp_matrix = matrix, times)
}

C_coxtime <- calculate_cindex(sampled_matrix_coxtime, surv_obj, 50)
C_deepsurv <- calculate_cindex(sampled_matrix_deepsurv, surv_obj, 50)
C_deephit <- calculate_cindex(matrix_deephit, surv_obj, 15)

IBS_coxtime <- calculate_ibs(sampled_matrix_coxtime, sampled_t, surv_obj)
IBS_deepsurv <- calculate_ibs(sampled_matrix_deepsurv, sampled_t, surv_obj)
IBS_deephit <- calculate_ibs(matrix_deephit[,-1], deephit_t[-1], surv_obj)

# Display results
data.frame(
  model = c("CoxTime", "DeepSurv", "DeepHit"),
  C_index = c(C_coxtime, C_deepsurv, C_deephit),
  IBS = c(IBS_coxtime, IBS_deepsurv, IBS_deephit)
)
```
### Survival Prediction

```{r tid gradient, fig.width=10, fig.height=15}
# Print instances of interest
tid_ids <- c(13, 387)
print(test[tid_ids, ])

# Compute Vanilla Gradient
grad_cox <- surv_grad(exp_coxtime, target = "survival", instance = tid_ids)
grad_deephit <- surv_grad(exp_deephit, target = "survival", instance = tid_ids)
grad_deepsurv <- surv_grad(exp_deepsurv, target = "survival", instance = tid_ids)

# Plot survival predictions
surv_plot <- cowplot::plot_grid(
  plot_surv_pred(grad_cox) ,
  plot_surv_pred(grad_deephit),
  plot_surv_pred(grad_deepsurv),
  nrow = 3, labels = c("CoxTime", "DeepHit", "DeepSurv"),
  label_x = 0.03,      
  label_size = 14) 
surv_plot

# Save plot
ggsave(
  "/Users/sophielangbein/Desktop/PhD/Survinng/plots_paper/surv_plot_tid.pdf",
  plot = surv_plot,
  width = 8,
  height = 14,
  device = "pdf"
)
```


### Gradient (Sensitivity)

```{r tid gradient, fig.width=10, fig.height=15}
# Plot attributions
grad_plot <- cowplot::plot_grid(
  plot_attribution(grad_cox) ,
  plot_attribution(grad_deephit),
  plot_attribution(grad_deepsurv),
  nrow = 3, labels = c("CoxTime", "DeepHit", "DeepSurv"))
grad_plot

# Save plot
ggsave(
  "/Users/sophielangbein/Desktop/PhD/Survinng/plots_paper/grad_plot_tid.pdf",
  plot = grad_plot,
  width = 10,
  height = 15,
  device = "pdf"
)
```

### SmoothGrad (Sensitivity)

```{r tid smoothgrad, fig.width=10, fig.height=15}
# Compute SmoothGrad
sg_cox <- surv_smoothgrad(exp_coxtime, target = "survival", instance = tid_ids, n = 50, noise_level = 0.1)
sg_deephit <- surv_smoothgrad(exp_deephit, target = "survival", instance = tid_ids, n = 50, noise_level = 0.1)
sg_deepsurv <- surv_smoothgrad(exp_deepsurv, target = "survival", instance = tid_ids, n = 50, noise_level = 0.1)

# Plot attributions
smoothgrad_plot <- cowplot::plot_grid(
  plot_attribution(sg_cox), 
  plot_attribution(sg_deephit), 
  plot_attribution(sg_deepsurv),
  nrow = 3, labels = c("CoxTime", "DeepHit", "DeepSurv"))
smoothgrad_plot

# Save plot
ggsave(
  "/Users/sophielangbein/Desktop/PhD/Survinng/plots_paper/smoothgrad_plot_tid.pdf",
  plot = smoothgrad_plot,
  width = 10,
  height = 15,
  device = "pdf"
)
```

### Gradient x Input

```{r tid gradientxinput, fig.width=10, fig.height=15}
# Compute GradientxInput
gradin_cox <- surv_grad(exp_coxtime, instance = tid_ids, times_input = TRUE)
gradin_deephit <- surv_grad(exp_deephit, instance = tid_ids, times_input = TRUE)
gradin_deepsurv <- surv_grad(exp_deepsurv, instance = tid_ids, times_input = TRUE)

# Plot attributions
gradin_plot <- cowplot::plot_grid(
  plot_attribution(gradin_cox), 
  plot_attribution(gradin_deephit), 
  plot_attribution(gradin_deepsurv),
  nrow = 3, labels = c("CoxTime", "DeepHit", "DeepSurv"))
gradin_plot

# Save plot
ggsave(
  "/Users/sophielangbein/Desktop/PhD/Survinng/plots_paper/gradin_plot_tid.pdf",
  plot = gradin_plot,
  width = 10,
  height = 15,
  device = "pdf"
)
```



### SmoothGrad x Input

```{r tid smoothgradxinput, fig.width=10, fig.height=15}
# Compute SmoothGradxInput
sgin_cox <- surv_smoothgrad(exp_coxtime, instance = tid_ids, n = 50, noise_level = 0.3,
                          times_input = TRUE)
sgin_deephit <- surv_smoothgrad(exp_deephit, instance = tid_ids, n = 50, noise_level = 0.3,
                              times_input = TRUE)
sgin_deepsurv <- surv_smoothgrad(exp_deepsurv, instance = tid_ids, n = 50, noise_level = 0.3,
                               times_input = TRUE)

# Plot attributions
smoothgradin_plot <- cowplot::plot_grid(
  plot_attribution(sgin_cox), 
  plot_attribution(sgin_deephit), 
  plot_attribution(sgin_deepsurv),
  nrow = 3, labels = c("CoxTime", "DeepHit", "DeepSurv"))
smoothgradin_plot

# Save plot
ggsave(
  "/Users/sophielangbein/Desktop/PhD/Survinng/plots_paper/smoothgradin_plot_tid.pdf",
  plot = smoothgradin_plot,
  width = 10,
  height = 15,
  device = "pdf"
)
```


### IntegratedGradient

## Zero baseline (should be proportional to Gradient x Input)

```{r tid intgrad0, fig.width=10, fig.height=15}
# Copute IntegratedGradient with 0 baseline
x_ref <- matrix(c(0,0,0), nrow = 1)
ig0_cox <- surv_intgrad(exp_coxtime, instance = tid_ids, n = 50, x_ref = x_ref)
ig0_deephit <- surv_intgrad(exp_deephit, instance = tid_ids, n = 50, x_ref = x_ref)
ig0_deepsurv <- surv_intgrad(exp_deepsurv, instance = tid_ids, n = 50, x_ref = x_ref)

# Plot attributions
intgrad0_plot <- cowplot::plot_grid(
  plot_attribution(ig0_cox), 
  plot_attribution(ig0_deephit), 
  plot_attribution(ig0_deepsurv),
  nrow = 3, labels = c("CoxTime", "DeepHit", "DeepSurv"))
intgrad0_plot 

# Save plot
ggsave(
  "/Users/sophielangbein/Desktop/PhD/Survinng/plots_paper/intgrad0_plot_tid.pdf",
  plot = intgrad0_plot,
  width = 10,
  height = 15,
  device = "pdf"
)
```

## Mean baseline

```{r tid intgradmean, fig.width=10, fig.height=15}
# Compute IntegratedGradient with mean baseline
x_ref <- NULL # default: feature-wise mean
igm_cox <- surv_intgrad(exp_coxtime, instance = tid_ids, n = 50, x_ref = x_ref)
igm_deephit <- surv_intgrad(exp_deephit, instance = tid_ids, n = 50, x_ref = x_ref)
igm_deepsurv <- surv_intgrad(exp_deepsurv, instance = tid_ids, n = 50, x_ref = x_ref)

# Plot attributions
intgradmean_plot <- cowplot::plot_grid(
  plot_attribution(igm_cox), 
  plot_attribution(igm_deephit), 
  plot_attribution(igm_deepsurv),
  nrow = 3, labels = c("CoxTime", "DeepHit", "DeepSurv"))
intgradmean_plot

# Save plot
ggsave(
  "/Users/sophielangbein/Desktop/PhD/Survinng/plots_paper/intgradmean_plot_tid.pdf",
  plot = intgradmean_plot,
  width = 10,
  height = 15,
  device = "pdf"
)
```

### GradShap

```{r tid gradshap, fig.width=10, fig.height=15}
# Copute GradShap
gshap_cox <- surv_gradSHAP(exp_coxtime, instance = tid_ids, n = 50, num_samples = 100, 
                           batch_size = 1000)
gshap_deephit <- surv_gradSHAP(exp_deephit, instance = tid_ids, n = 50, num_samples = 100, 
                           batch_size = 1000)
gshap_deepsurv <- surv_gradSHAP(exp_deepsurv, instance = tid_ids, n = 50, num_samples = 100, 
                           batch_size = 1000)

# Plot attributions
gshap_plot <- cowplot::plot_grid(
  plot_attribution(gshap_cox), 
  plot_attribution(gshap_deephit), 
  plot_attribution(gshap_deepsurv),
  nrow = 3, labels = c("CoxTime", "DeepHit", "DeepSurv"))
gshap_plot 

# Save plot
ggsave(
  "/Users/sophielangbein/Desktop/PhD/Survinng/plots_paper/gshap_plot_tid.pdf",
  plot = gshap_plot,
  width = 10,
  height = 15,
  device = "pdf"
)
```


### Time-dependent effects

## Generate the data

Simulation setting:
- $10,000$ samples ($9,500$ for training, $500$ for testing)
- $X_1 \sim \mathcal{N}(0,1)$ has a time-dependent effect: first negative, then positive on hazard (vice versa on survival)
- $X_2 \sim \mathcal{N}(0,1)$ has a positive effect on the hazard -> negative effect on survival
- $X_3 \sim \mathcal{U}(0,1)$ has a stronger negative effect on the hazard -> positive effect on survival
- $X_3 \sim \mathcal{U}(-1,1)$ has no effect

```{r td data generation}
set.seed(42)

# Simulate data
n <- 10000
x <- data.frame(x1 = runif(n, 0, 1), x2 = rnorm(n), x3 = rnorm(n), x4 = runif(n,-1,1))

simdat <- simsurv(dist = "weibull", lambdas = 0.1, gammas = 1.5, betas = c(x1 = -3, x2 = 1.7, x3 = -2.4), x = x, tde = c(x1 = 6), tdefunction = "log", maxt = 7)
y <- simdat[, -1]
colnames(y)[1] <- "time"
dat <- cbind(y, x)

# Train/test
idx <- sample(n, 9500)
train <- dat[idx, ]
test <- dat[-idx, ]
```

## Fit the models
```{r td, echo = FALSE}
fit_model <- function(model, train, test) {
  callr::r(function(model, train, test) {
    library(survivalmodels)
    library(survival)
    reticulate::use_condaenv("Survinng", required = TRUE)
    set.seed(1)
    set_seed(1)
    
    # Fit model
    if (model == "CoxTime") {
      model <- coxtime(Surv(time, status) ~ ., data = train, verbose = FALSE, epochs = 500L,
                     early_stopping = TRUE, frac = 0.33, batch_size = 1024L, patience = 10L,
                     dropout = 0.1)
    } else if (model == "DeepHit") {
      model <- deephit(Surv(time, status) ~ ., data = train, verbose = FALSE, epochs = 500L,
                     early_stopping = TRUE, frac = 0.33, patience = 10L, cuts = 30, 
                     batch_size = 1024L, dropout = 0.1)
    } else if (model == "DeepSurv") {
      model <- deepsurv(Surv(time, status) ~ ., data = train, verbose = FALSE, epochs = 100L,
                      early_stopping = TRUE, frac = 0.33, patience = 10L, batch_size = 1024L,
                      dropout = 0.1)
    } else {
      stop("Model not found")
    }
    
    # Make predictions
    pred <- predict(model, newdata = test, type = "survival")
    dat <- data.frame(
      pred = c(pred), 
      time = rep(as.numeric(colnames(pred)), each = nrow(pred)),
      id = rep(1:nrow(pred), ncol(pred))
    )
    list(Survinng::extract_model(model), pred = dat)
  }, list(model, train, test))
}
```

```{r td fit models, fig.width=10, fig.height=15}
# Fit the models
ext_deephit <- fit_model("DeepHit", train, test)
ext_coxtime <- fit_model("CoxTime", train, test)
ext_deepsurv <- fit_model("DeepSurv", train, test)
```

## Create Explainer

```{r td explainer}
library(Survinng)
library(torch)

# Create explainer
exp_deephit <- Survinng::explain(ext_deephit[[1]], data = test)
exp_coxtime <- Survinng::explain(ext_coxtime[[1]], data = test)
exp_deepsurv <- Survinng::explain(ext_deepsurv[[1]], data = test)
```


## Performance Measures

```{r tid performance measures, fig.width=8, fig.height=8}
# Define a function to reshape data into a wide matrix format
prepare_matrix <- function(data, id_col = "id", time_col = "time", pred_col = "pred") {
  wide_data <- data %>%
    pivot_wider(names_from = {{time_col}}, values_from = {{pred_col}})
  
  # Convert the specified column to row names and remove it from the data
  wide_data <- as.data.frame(wide_data)
  rownames(wide_data) <- wide_data[[id_col]]
  wide_data <- wide_data[, -which(names(wide_data) == id_col)]
  
  # Convert to a matrix
  as.matrix(wide_data)
}

# Prepare matrices
matrix_coxtime <- prepare_matrix(ext_coxtime$pred)
matrix_deepsurv <- prepare_matrix(ext_deepsurv$pred)
matrix_deephit <- prepare_matrix(ext_deephit$pred)[,-1]

# Define survival object
surv_obj <- Surv(test$time, test$status)

# Define time indices and sampled time
t_interest <- sort(unique(ext_coxtime$pred$time))
num_samples <- 100
indices <- round(seq(1, length(t_interest), length.out = num_samples))
sampled_t <- t_interest[indices]
deephit_t <- sort(unique(ext_deephit$pred$time))[-1]

# Sample matrices
sampled_matrix_coxtime <- matrix_coxtime[, indices]
sampled_matrix_deepsurv <- matrix_deepsurv[, indices]

# Calculate Brier scores in a single step
calculate_brier <- function(matrix, times, surv_obj) {
  sapply(1:ncol(matrix), function(i) Brier(surv_obj, pre_sp = matrix[, i], times[i]))
}

metrics_coxtime <- calculate_brier(sampled_matrix_coxtime, sampled_t, surv_obj)
metrics_deepsurv <- calculate_brier(sampled_matrix_deepsurv, sampled_t, surv_obj)
metrics_deephit <- calculate_brier(matrix_deephit, deephit_t, surv_obj)

# Combine results into a single data frame for plotting
combine_results <- function(metrics, times, model_name) {
  data.frame(time = times, BS = metrics, model = model_name)
}

data_coxtime <- combine_results(metrics_coxtime, sampled_t, "CoxTime")
data_deepsurv <- combine_results(metrics_deepsurv, sampled_t, "DeepSurv")
data_deephit <- combine_results(metrics_deephit, deephit_t, "DeepHit")
data_BS <- rbind(data_coxtime, data_deepsurv, data_deephit)

# Plot Brier scores
colorblind_palette <- c("CoxTime" = "#E69F00", "DeepSurv" = "#56B4E9", "DeepHit" = "#009E73")

brier_plot_td <- ggplot(data_BS, aes(x = time, y = BS, color = model, linetype = model)) +
  geom_line() +
  scale_color_manual(values = colorblind_palette) +  # Apply custom colors
  scale_linetype_manual(values = c("CoxTime" = "solid", "DeepSurv" = "dashed", "DeepHit" = "dotted")) + 
  labs(title = "Brier Score over Time", x = "Time", y = "Brier Score") +
  theme_minimal(base_size = 16)
brier_plot_td 

# Save plot
ggsave(
  "/Users/sophielangbein/Desktop/PhD/Survinng/plots_paper/brier_plot_td.pdf",
  plot = brier_plot_td,
  width = 8,
  height = 8,
  device = "pdf"
)

# Calculate C-index and IBS for each model
calculate_cindex <- function(matrix, surv_obj, index) {
  Cindex(surv_obj, predicted = matrix[, index])
}

calculate_ibs <- function(matrix, times, surv_obj) {
  IBS(surv_obj, sp_matrix = matrix, times)
}

C_coxtime <- calculate_cindex(sampled_matrix_coxtime, surv_obj, 50)
C_deepsurv <- calculate_cindex(sampled_matrix_deepsurv, surv_obj, 50)
C_deephit <- calculate_cindex(matrix_deephit, surv_obj, 15)

IBS_coxtime <- calculate_ibs(sampled_matrix_coxtime, sampled_t, surv_obj)
IBS_deepsurv <- calculate_ibs(sampled_matrix_deepsurv, sampled_t, surv_obj)
IBS_deephit <- calculate_ibs(matrix_deephit[,-1], deephit_t[-1], surv_obj)

# Display results
data.frame(
  model = c("CoxTime", "DeepSurv", "DeepHit"),
  C_index = c(C_coxtime, C_deepsurv, C_deephit),
  IBS = c(IBS_coxtime, IBS_deepsurv, IBS_deephit)
)
```

## Kaplan-Meier Survival Curves

```{r tid KM, fig.width=8, fig.height=8}
# Categorize `x1` into bins (e.g., low, medium, high)
dat$x1_group <- cut(dat$x1, 
                    breaks = quantile(dat$x1, probs = c(0, 0.5, 1)), 
                    labels = c("Low", "High"), 
                    include.lowest = TRUE)

# Create a Surv object
surv_obj <- Surv(dat$time, dat$status)

# Fit Kaplan-Meier survival curves stratified by `x1_group`
km_fit <- survfit(surv_obj ~ x1_group, data = dat)

# Plot the KM curves
km_plot <- ggsurvplot(km_fit, 
           data = dat,
           xlab = "Time",
           ylab = "Survival Probability",
           legend.title = "x1 Group",
           palette = c("#377EB8", "#E69F00"),  
           title = "Kaplan-Meier Survival Curves") 
km_plot$plot <- km_plot$plot + 
                theme_minimal(base_size = 16) +
                theme(
                  legend.position = "bottom"
                  )
km_plot

# Save plot
ggsave(
  "/Users/sophielangbein/Desktop/PhD/Survinng/plots_paper/km_plot.pdf",
  plot = km_plot$plot,
  width = 8,
  height = 8,
  device = "pdf"
)
```

### Survival Prediction

```{r td gradient, fig.width=10, fig.height=15}
# Print instances of interest
td_ids <- c(79, 428)
print(test[td_ids, ])

# Compute Vanilla Gradient
grad_cox <- surv_grad(exp_coxtime, target = "survival", instance = td_ids)
grad_deephit <- surv_grad(exp_deephit, target = "survival", instance = td_ids)
grad_deepsurv <- surv_grad(exp_deepsurv, target = "survival", instance = td_ids)

# Plot survival predictions
surv_plot <- cowplot::plot_grid(
  plot_surv_pred(grad_cox) ,
  plot_surv_pred(grad_deephit),
  plot_surv_pred(grad_deepsurv),
  nrow = 3, labels = c("CoxTime", "DeepHit", "DeepSurv"),
  label_x = 0.03,      
  label_size = 14) 
surv_plot

# Save plot
ggsave(
  "/Users/sophielangbein/Desktop/PhD/Survinng/plots_paper/surv_plot_td.pdf",
  plot = surv_plot,
  width = 8,
  height = 14,
  device = "pdf"
)
```
### Gradient (Sensitivity)

```{r td gradient, fig.width=10, fig.height=15}
# Plot attributions
grad_plot <- cowplot::plot_grid(
  plot_attribution(grad_cox) ,
  plot_attribution(grad_deephit),
  plot_attribution(grad_deepsurv),
  nrow = 3, labels = c("CoxTime", "DeepHit", "DeepSurv"))
grad_plot

# Save plot
ggsave(
  "/Users/sophielangbein/Desktop/PhD/Survinng/plots_paper/grad_plot_td.pdf",
  plot = grad_plot,
  width = 10,
  height = 15,
  device = "pdf"
)
```

### SmoothGrad (Sensitivity)

```{r td smoothgrad, fig.width=10, fig.height=15}
# Compute SmoothGrad
sg_cox <- surv_smoothgrad(exp_coxtime, target = "survival", instance = td_ids, n = 50, noise_level = 0.1)
sg_deephit <- surv_smoothgrad(exp_deephit, target = "survival", instance = td_ids, n = 50, noise_level = 0.1)
sg_deepsurv <- surv_smoothgrad(exp_deepsurv, target = "survival", instance = td_ids, n = 50, noise_level = 0.1)

# Plot attributions
smoothgrad_plot <- cowplot::plot_grid(
  plot_attribution(sg_cox), 
  plot_attribution(sg_deephit), 
  plot_attribution(sg_deepsurv),
  nrow = 3, labels = c("CoxTime", "DeepHit", "DeepSurv"))
smoothgrad_plot

# Save plot
ggsave(
  "/Users/sophielangbein/Desktop/PhD/Survinng/plots_paper/smoothgrad_plot_td.pdf",
  plot = smoothgrad_plot,
  width = 10,
  height = 15,
  device = "pdf"
)
```

### Gradient x Input

```{r td gradientxinput, fig.width=10, fig.height=15}
# Compute GradientxInput
gradin_cox <- surv_grad(exp_coxtime, instance = td_ids, times_input = TRUE)
gradin_deephit <- surv_grad(exp_deephit, instance = td_ids, times_input = TRUE)
gradin_deepsurv <- surv_grad(exp_deepsurv, instance = td_ids, times_input = TRUE)

# Plot attributions
gradin_plot <- cowplot::plot_grid(
  plot_attribution(gradin_cox), 
  plot_attribution(gradin_deephit), 
  plot_attribution(gradin_deepsurv),
  nrow = 3, labels = c("CoxTime", "DeepHit", "DeepSurv"))
gradin_plot

# Save plot
ggsave(
  "/Users/sophielangbein/Desktop/PhD/Survinng/plots_paper/gradin_plot_td.pdf",
  plot = gradin_plot,
  width = 10,
  height = 15,
  device = "pdf"
)
```

### SmoothGrad x Input

```{r td smoothgradxinput, fig.width=10, fig.height=15}
# Compute SmoothGradxInput
sgin_cox <- surv_smoothgrad(exp_coxtime, instance = td_ids, n = 50, noise_level = 0.3,
                          times_input = TRUE)
sgin_deephit <- surv_smoothgrad(exp_deephit, instance = td_ids, n = 50, noise_level = 0.3,
                              times_input = TRUE)
sgin_deepsurv <- surv_smoothgrad(exp_deepsurv, instance = td_ids, n = 50, noise_level = 0.3,
                               times_input = TRUE)

# Plot attributions
smoothgradin_plot <- cowplot::plot_grid(
  plot_attribution(sgin_cox), 
  plot_attribution(sgin_deephit), 
  plot_attribution(sgin_deepsurv),
  nrow = 3, labels = c("CoxTime", "DeepHit", "DeepSurv"))
smoothgradin_plot

# Save plot
ggsave(
  "/Users/sophielangbein/Desktop/PhD/Survinng/plots_paper/smoothgradin_plot_td.pdf",
  plot = smoothgradin_plot,
  width = 10,
  height = 15,
  device = "pdf"
)
```

### IntegratedGradient

## Zero baseline (should be proportional to Gradient x Input)

```{r td intgrad0, fig.width=10, fig.height=15}
# Copute IntegratedGradient with 0 baseline
x_ref <- matrix(c(0,0,0,0), nrow = 1)
ig0_cox <- surv_intgrad(exp_coxtime, instance = td_ids, n = 50, x_ref = x_ref)
ig0_deephit <- surv_intgrad(exp_deephit, instance = td_ids, n = 50, x_ref = x_ref)
ig0_deepsurv <- surv_intgrad(exp_deepsurv, instance = td_ids, n = 50, x_ref = x_ref)

# Plot attributions
intgrad0_plot <- cowplot::plot_grid(
  plot_attribution(ig0_cox), 
  plot_attribution(ig0_deephit), 
  plot_attribution(ig0_deepsurv),
  nrow = 3, labels = c("CoxTime", "DeepHit", "DeepSurv"))
intgrad0_plot 

# Save plot
ggsave(
  "/Users/sophielangbein/Desktop/PhD/Survinng/plots_paper/intgrad0_plot_td.pdf",
  plot = intgrad0_plot,
  width = 10,
  height = 15,
  device = "pdf"
)
```


## Mean baseline

```{r td intgradmean, fig.width=10, fig.height=15}
# Compute IntegratedGradient with mean baseline
x_ref <- NULL # default: feature-wise mean
igm_cox <- surv_intgrad(exp_coxtime, instance = td_ids, n = 50, x_ref = x_ref)
igm_deephit <- surv_intgrad(exp_deephit, instance = td_ids, n = 50, x_ref = x_ref)
igm_deepsurv <- surv_intgrad(exp_deepsurv, instance = td_ids, n = 50, x_ref = x_ref)

# Plot attributions
intgradmean_plot <- cowplot::plot_grid(
  plot_attribution(igm_cox), 
  plot_attribution(igm_deephit), 
  plot_attribution(igm_deepsurv),
  nrow = 3, labels = c("CoxTime", "DeepHit", "DeepSurv"))
intgradmean_plot

# Save plot
ggsave(
  "/Users/sophielangbein/Desktop/PhD/Survinng/plots_paper/intgradmean_plot_td.pdf",
  plot = intgradmean_plot,
  width = 10,
  height = 15,
  device = "pdf"
)
```


### GradShap

```{r tid gradshap, fig.width=10, fig.height=15}
# Compute GradShap
gshap_cox <- surv_gradSHAP(exp_coxtime, instance = td_ids, n = 50, num_samples = 100, 
                           batch_size = 1000)
gshap_deephit <- surv_gradSHAP(exp_deephit, instance = td_ids, n = 50, num_samples = 100, 
                           batch_size = 1000)
gshap_deepsurv <- surv_gradSHAP(exp_deepsurv, instance = td_ids, n = 50, num_samples = 100, 
                           batch_size = 1000)

# Plot attributions
gshap_plot <- cowplot::plot_grid(
  plot_attribution(gshap_cox), 
  plot_attribution(gshap_deephit), 
  plot_attribution(gshap_deepsurv),
  nrow = 3, labels = c("CoxTime", "DeepHit", "DeepSurv"))
gshap_plot 

# Save plot
ggsave(
  "/Users/sophielangbein/Desktop/PhD/Survinng/plots_paper/gshap_plot_td.pdf",
  plot = gshap_plot,
  width = 10,
  height = 15,
  device = "pdf"
)
```

